%*******************************************************
% Acknowledgments
%*******************************************************
\refstepcounter{dummy}
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\null
\vspace{4\onelineskip}

\fancyquote{Isaac Newton}{%
    If I have seen further, it is by standing on the shoulders of giants.
}

\vspace{2\onelineskip}

\begingroup
\let\clearpage\relax

\section*{Acknowledgments}

I strongly believe that we can only succeed through collaboration, be it in science, or in life. Thus, I am deeply grateful to anyone who has helped me on my path so far. This includes anyone who has proofread this document, offered advice, inspired, or instructed me. 

I thank \emph{Kurt Roth} for his courage to supervise me abroad, without expecting anything in return. Likewise, I thank \emph{Markus Jochum} for welcoming me as a Master's student without ever having met me before (and without me knowing much about Physical Oceanography). I thank the free software movement (and, really, anyone who puts their code on GitHub) for providing scientists, artists, students, or just hobbyists with powerful tools without expecting any compensation. I even thank anyone who answers random strangers' questions on the Internet. Because knowledge, like happiness, is only real when shared.

Likewise, if you have questions regarding this document, the codes I used, or just want to chat --- I'm happy to share: \href{mailto:mail@dionhaefner.de}{mail@dionhaefner.de}.
\endgroup